\documentclass[a4paper,12pt]{article}
\usepackage{url}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
%\usepackage{mdframed}
\usepackage{adjustbox}
\usepackage{markdown}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

%\lstset{frame=tb,
%	language=C++,
%	aboveskip=3mm,
%	belowskip=3mm,
%	showstringspaces=false,
%	columns=flexible,
%	basicstyle={\small\ttfamily},
%	numbers=none,
%	numberstyle=\tiny\color{gray},
%	keywordstyle=\color{blue},
%	commentstyle=\color{dkgreen},
%	stringstyle=\color{mauve},
%	breaklines=true,
%	breakatwhitespace=true,
%	tabsize=3
%}
\begin{document}
	
	\title{CMPE - 382 Operating Systems }
	\author{Homework}
	\date{Spring 2023}
	\maketitle
	\section*{Guidelines}
	
	You need to submit this homework on  {\color{blue}19th May at 10pm}, on LMS. Late submissions are not allowed, and will be marked zero. 

	
	\begin{itemize}
		\item You need to do this homework in a group of up to 4 students. 
		\item In the exceptional cases, you can make group of 5 students, but you have to implement some added functionality in the task. You can provide it as Deliverable 4 of the homework, also create a text file in Deliverable 4 folder that details what you have provided as extra functionality. 
		\item You may form the group with other sections as well. 
		\item Clearly report group member names in \path{Group Member Information.xlsx} file, given along with this homework. 
		\item You will submit your homework to LMS (only one member of the group will submit).
		\item Implement each deliverable in its corresponding folder, and submit all the folders in a single zip file on LMS.
		\item It is better to submit incomplete assignment than none at all.
		\item It is strongly advised that you start working on the assignment the day you get it. Assignments WILL take time.
		\item Every assignment you submit should be a single zipped file containing all the other files. 
%Suppose your name is John Doe and your id is 0022 so the name of the submitted file should be JohnDoe0022.zip
		\item DO NOT send your assignment to your instructor over email. It won't be considered for evaluation. 
		\item You can be called in for Viva for any assignment that you submit
%		\item There are two questions in this homework, both carry equal marks. 
		\item This homework is 25\% worth of overall grade. Each deliverable carry equal percentage of marks.
	\end{itemize}
	
	
\markdownInput{README.md}	
	
\end{document}